Precision calculations of the cosmic shear power spectrum projection

### 2017-02-14 limber2.tex
Plots updated

  \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
for the ExtL2Sph projection using the Hankel transform (green line), compared
to the spherical Legendre transform of the same projection (blue squares), and
the FullSph projection (red circles). \emph{Left panel:} The relative
difference with respect to the full spherical case (FullSph with Legendre
transformation) of ExtL2Sph with Hankel transform (green line), and ExtL2Sph
with Legendre transform (blue squares).}

>>>>

  \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
for the ExtL2Sph projection using the spherical Legendre transform (green line for ExtL2Sph, grey squares for FullSph),
compared to the flat-sky Hankel transform of ExtL2Sph (red circles).
\emph{Left panel:} The relative
difference with respect to the full spherical case (FullSph with Legendre
transformation) of ExtL2Sph with Legendre (green line), 
and Hankel transform (red circles).}
